\documentclass{amsart}
\usepackage{accents,amsmath,amssymb,amsthm,xeCJK}
\setCJKmainfont{SimHei}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}[proposition]{Lemma}
\newtheorem{theorem}[proposition]{Theorem}
\newtheorem{conjecture}[proposition]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[proposition]{Definition}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\newcommand{\lring}[1]{\accentset{\circ}{#1}}
\newcommand{\ltilde}[1]{\accentset{\sim}{#1}}

\title{On the simpleness of convex closed curves}
\author{Scallop Ye}

\begin{document}

\begin{abstract}
    A convex curve is a plane curve whose intersection with a
    line is either a set of at most two points or a line segment.
    With analytical definitions of convexity and simpleness,
    we show that a convex closed curve is simple
    if and only if it does not lie on a line.
    We conjecture that the same result still holds when
    geometrical definitions are used instead.
\end{abstract}

\maketitle

\section{Definitions}

We first follow Milnor \cite{milnor} to
define the concepts in a rigorous manner.

\begin{definition}[Closed curves]
    A \emph{closed curve} in Euclidean $n$-space $\mathbb{E}^n$
    is a nonconstant continuous periodic function
    $\gamma:\mathbb{R}\to\mathbb{R}^n$. We say that a closed curve
    is \emph{planar} iff its image lies on a line or in a plane.
\end{definition}

Here we do not restrict a closed curve to be light\footnote{
    A continuous function $f:S_1\to S_2$ is called \emph{light}
    iff $f^{-1}(y)$ is totally disconnected for each $y\in S_2$
    (see \cite[Definition 13.1]{nadler}). A closed curve
    is light iff it is not constant on any interval.
}, considering that every closed curve may be
reparameterized to be light, as we will see in Section
\ref{sec:geometrical_consideration}.

One can show that a closed curve has a least positive period.
For convenience we redefine the notion of period for closed curves
as follows.

\begin{definition}[Periods]
    Let $\gamma$ be a closed curve of least positive period $p$,
    and let $x\in\mathbb{R}$. We call $p$ \emph{the period} of $\gamma$,
    and the interval $P:=[x,x+p)$ \emph{a period} of $\gamma$.
    We say that a closed curve $\gamma'$ is \emph{of period} $p'$
    iff the period of $\gamma'$ is $p'$.
\end{definition}

In fact, every closed curve $\gamma$ of period $p$
can be factored into a unique pair of functions
$(\lring{\gamma}:\mathbb{S}^1\to\mathbb{R}^n,
    \ltilde{\gamma}:\mathbb{R}\to\mathbb{S}^1)$
such that $\gamma=\lring{\gamma}\circ\ltilde{\gamma}$,
where $\lring{\gamma}$ is a nonconstant continuous function
and $\ltilde{\gamma}$ is another closed curve
$\ltilde{\gamma}(t):=(\cos 2\pi t/p,\sin 2\pi t/p)$
whose image is the unit circle $\mathbb{S}^1$. We may call
$\lring{\gamma}$ the \emph{equivalent circular map} of $\gamma$,
call $\ltilde{\gamma}$ the \emph{underlying circle} of $\gamma$,
and fix these notations.

Note that the restriction of $\ltilde{\gamma}$ to
every period of $\gamma$ is continuous and bijective.
This fact allows us to translate between
the properties of a closed curve $\gamma$
(on individual periods) and of its equivalent circular map
$\lring{\gamma}$ (on the unit circle).

\begin{definition}[Simpleness]
    Let $\gamma$ be a closed curve of period $p$.
    We say that $\gamma$ is \emph{simple}
    iff for all $t_1,t_2\in\mathbb{R}$, $\gamma(t_1)=\gamma(t_2)$
    only when $(t_1-t_2)/p$ is an integer.
\end{definition}

\begin{proposition}
    \label{pro:simple_equiv}
    Let $\gamma$ be a closed curve.
    Then the following are equivalent:
    \begin{enumerate}
        \item $\gamma$ is simple.
        \item $\lring{\gamma}$ is a homeomorphism.
        \item For every period $P$ of $\gamma$, the restriction
              of $\gamma$ to $P$ is injective.
        \item There exists a period $P$ of $\gamma$ such that
              the restriction of $\gamma$ to $P$ is injective.
    \end{enumerate}
\end{proposition}

\begin{proof}
    The claim follows immediately from the definitions above.
\end{proof}

\begin{proposition}
    \label{pro:simple_suf_cond}
    Let $f:\mathbb{R}\to\mathbb{R}^n$
    be a continuous periodic function,
    and let $p>0$ be a period of $f$. Suppose that
    the restriction of $f$ to some interval $[x_0,x_0+p)$
    is injective.
    Then $f$ is a simple closed curve of period $p$.
\end{proposition}

\begin{proof}
    The restriction being injective implies that
    $f$ is nonconstant and that $p$ is the least positive
    period of $f$. Thus $f$ is a closed curve of period $p$.
    Then by Proposition \ref{pro:simple_equiv}
    we know that $f$ is simple.
\end{proof}

We now present a unified definition of convex closed curves in
all dimensions. Later we will show that the property of convexity
implies planarity and is preserved under a bijective affine map
(thus consistent across all dimensions).

\begin{definition}[Convexity]
    Let $\gamma$ be a closed curve in $\mathbb{E}^n$.
    We say that $\gamma$ is \emph{convex} iff
    for every hyperplane $H\subset\mathbb{R}^n$,
    the inverse image $\lring{\gamma}^{-1}(H)$ either
    has cardinality $\le2$, is a nondegenerate arc,
    or is the unit circle $\mathbb{S}^1$.
\end{definition}

\begin{proposition}
    \label{pro:convex_equiv}
    A closed curve $\gamma$ in $\mathbb{E}^n$ is convex
    iff for every $u\in\mathbb{S}^{n-1}$ and $y\in\mathbb{R}$,
    there exists a period $P$ of $\gamma$ such that
    the set $\{t\in P:u\cdot\gamma(t)=y\}$ either
    has cardinality $\le2$ or is a nondegenerate interval.
\end{proposition}

\begin{proof}
    Suppose that there exists a hyperplane $H\subset\mathbb{R}^n$
    such that $\lring{\gamma}^{-1}(H)$ is neither an arc
    nor $\mathbb{S}^1$, and if it is finite, has cardinality $>2$.
    Then we can find a normal vector $u\in\mathbb{S}^{n-1}$ and an
    offset $y\in\mathbb{R}$ such that
    $H=\{x\in\mathbb{R}^n:u\cdot x=y\}$.
    We claim that there does not exist a period $P$ of $\gamma$
    such that the set $T:=\{t\in P:u\cdot\gamma(t)=y\}$
    either has cardinality $\le2$ or is a nondegenerate interval,
    because otherwise
    \[\lring{\gamma}^{-1}(H)
        =\ltilde{\gamma}(\gamma^{-1}(H))
        =\ltilde{\gamma}(\gamma^{-1}(H)\cap P)
        =\ltilde{\gamma}(T)\]
    would either have cardinality $\le2$
    (when $T$ has cardinality $\le2$),
    be a nondegenerate arc (when $T$ is a nondegenerate
    proper subinterval of $P$),
    or be $\mathbb{S}^1$ (when $T=P$).

    Now suppose that there exists $u\in\mathbb{S}^{n-1}$ and
    $y\in\mathbb{R}$ such that for every period $P$ of $\gamma$,
    the set $T:=\{t\in P:u\cdot\gamma(t)=y\}$ is not an interval,
    and if it is finite, has cardinality $>2$.
    Let $H$ be the hyperplane $H:=\{x\in\mathbb{R}^n:u\cdot x=y\}$.
    Then $\lring{\gamma}^{-1}(H)$ is neither an arc nor
    $\mathbb{S}^1$, and if it is finite, has cardinality $>2$,
    since otherwise \[T=\gamma^{-1}(H)\cap P
        =\ltilde{\gamma}^{-1}(\lring{\gamma}^{-1}(H))\cap P\]
    would either have cardinality $\le2$ for any period $P$ of
    $\gamma$ (when $\lring{\gamma}^{-1}(H)$ has cardinality $\le2$),
    be a nondegenerate proper subinterval of $P$ for some period
    $P:=[x_0,x_0+p)$ of $\gamma$ such that
    $\ltilde{\gamma}(x_0)\notin\lring{\gamma}^{-1}(H)$
    (when $\lring{\gamma}^{-1}(H)$ is a nondegenerate arc),
    or be $P$ for any period $P$ of $\gamma$
    (when $\lring{\gamma}^{-1}(H)=\mathbb{S}^1$).
\end{proof}

\begin{proposition}
    \label{pro:convex_planar}
    A convex closed curve is planar.
\end{proposition}

\begin{proof}
    Let $\gamma$ be a closed curve in $\mathbb{E}^n$ ($n\ge 3$) which
    is not planar, and let $P$ be any period of $\gamma$.
    Then there exists $c_1<c_2<c_3<c_4\in P$ such that the points
    $p_1:=\gamma(c_1),p_2:=\gamma(c_2),
        p_3:=\gamma(c_3),p_4:=\gamma(c_4)$
    are noncoplanar. Observe that every plane in $\mathbb{R}^n$
    can be written as an intersection of hyperplanes, and so
    we can find a hyperplane $H\subset\mathbb{R}^n$
    such that $p_1,p_3,p_4\in H$ but $p_2\notin H$. Now let
    $u\in\mathbb{S}^{n-1}$ be a vector normal to $H$. Since
    $u\cdot\gamma(c_1)=u\cdot\gamma(c_3)=u\cdot\gamma(c_4)
        \ne u\cdot\gamma(c_2)$,
    the set $\{t\in P:u\cdot\gamma(t)=y\}$ is not an interval,
    and if it is finite, has cardinality $>2$. Hence $\gamma$
    is not convex by Proposition \ref{pro:convex_equiv}.
\end{proof}

\begin{proposition}
    \label{pro:convex_preserved}
    Let $1\le n\le m$ be integers, let $\gamma$ be a closed curve
    in $\mathbb{E}^n$ of image $C$, and let $\gamma'$ be a closed curve
    in $\mathbb{E}^m$ of image $C'$ such that $C'\subset F$
    for some $n$-flat $F\subset\mathbb{R}^m$.
    Suppose that there exists a bijective affine map
    $f:\mathbb{R}^n\to F$ such that $\gamma'=f\circ\gamma$.
    Then $\gamma$ is convex iff $\gamma'$ is convex.
\end{proposition}

\begin{proof}[Sketch of proof]
    Suppose that $\gamma$ is not convex.
    Then there exists a hyperplane $H\subset\mathbb{R}^n$
    such that $\lring{\gamma}^{-1}(H)$ is neither an arc
    nor $\mathbb{S}^1$, and if it is finite, has cardinality $>2$.
    We can find a hyperplane $H'\subset\mathbb{R}^m$ such that
    $F\cap H'=f(H)$ (why?). It only remains to show that
    $\lring{\gamma}'^{-1}(H')=\lring{\gamma}^{-1}(H)$.

    Now suppose that $\gamma'$ is not convex.
    Then there exists a hyperplane $H'\subset\mathbb{R}^m$
    such that $\lring{\gamma}'^{-1}(H')$ is neither an arc
    nor $\mathbb{S}^1$, and if it is finite, has cardinality $>2$.
    The intersection $F\cap H'$ must be an $(n-1)$-flat
    in $\mathbb{R}^m$ (why?), so the inverse image
    $H:=f^{-1}(H')$ is a hyperplane in $\mathbb{R}^n$.
    It only remains to show that
    $\lring{\gamma}^{-1}(H)=\lring{\gamma}'^{-1}(H')$.
\end{proof}

We then prove a generalization of the necessity part
of \cite[Lemma 3.3]{milnor} in the hope that
our definitions are equivalent to Milnor's.

\begin{definition}
    Let $\gamma$ be a closed curve in $\mathbb{E}^n$,
    let $u\in\mathbb{S}^{n-1}$,
    and let $P$ be any period of $\gamma$.
    Define $\mu(\gamma,u)$ to be the cardinality of the set
    $\{t\in P:\text{the function }u\cdot\gamma
        \text{ attains a local maximum at }t\}$
    if it is finite, or $\infty$ otherwise.
\end{definition}

\begin{proposition}
    Let $\gamma$ be a closed curve in $\mathbb{E}^n$.
    If $\gamma$ is convex, then for every $u\in\mathbb{S}^{n-1}$
    either $\mu(\gamma,u)=1$ or $\mu(\gamma,u)=\infty$.
\end{proposition}

\begin{proof}
    Suppose that $2\le\mu(\gamma,u)<\infty$
    for some $u\in\mathbb{S}^{n-1}$.
    Let $f:\mathbb{R}\to\mathbb{R}$ be the function $u\cdot\gamma$,
    let $P:=[x,x+p)$ be any period of $\gamma$, and let $t_1<t_2\in P$
    such that $f$ attains local maxima at $t_1$ and $t_2$.
    Suppose that $f(t_1)\ge f(t_2)$.
    Since $f$ attains a finite number of local maxima in $P$,
    there exists $a,b,y$ with $t_1<a<t_2<b<x+p$ such that
    $f(a),f(b)<y<f(t_2)\le f(t_1)$.
    By the intermediate value theorem there exists
    $c_1\in(t_1,a)$, $c_2\in(a,t_2)$, and $c_3\in(t_2,b)$ such that
    $f(c_i)=y$ for $i=1,2,3$. Since $f(t_2)\ne y$, we know that
    $\gamma$ is not convex, a contradiction.

    Now suppose that $f(t_1)<f(t_2)$.
    If $t_1\ne x$ then the proof is identical,
    so we assume that $t_1=x$. Take $\delta:=(x+p-t_2)/2$.
    Similarly, there exists $c_1,c_2,c_3,y$ with
    $x-\delta<c_1<t_1=x<c_2<c_3<t_2<x+p-\delta$
    and $y<f(t_1)<f(t_2)$ such that
    $f(c_i)=y$ for $i=1,2,3$.
    Let $c_4:=c_1+p$ and obtain $f(c_4)=y$ with $c_4\in(t_2,x+p)$.
    Since $f(t_2)\ne y$, we again have a contradiction.
\end{proof}

The sufficiency part of the lemma seems way more tricky to prove
analytically, especially the case when $\mu(\gamma,u)=\infty$.
Milnor's proof, on the other hand, made too much use of
geometrical methods despite his analytical definitions.
It is not entirely clear, for example, why it is always possible
to rotate a line about one of its points of intersection with
a polygon so that the number of intersections is not decreased.
Also, we have this particular case when a polygon in the shape of 凸
(lit. convex; however the shape itself is concave)
is intersected by a horizontal line: the set of points of intersection
either has cardinality 2 or is infinite, but when infinite
the set may still be disconnected. This case is not seen to
be handled in Milnor's proof and does not seem trivial otherwise.
I think, however, that the lemma is true but still needs
an analytical proof for the sake of completeness.

\section{Analytical Proof}

Now that we have checked the equivalence of definitions,
we shall first present a lemma and then our main theorem.
Note that it suffices to give proofs for the two-dimensional case
as a convex closed curve is planar.

\begin{lemma}
    \label{lem}
    Let $f:(a,b)\cup(b,c)\to\mathbb{R}^2$ be a
    nonconstant function, and let $p\in\mathbb{R}^2$.
    Suppose that there exists $x_1,x_2\in(a,b)\cup(b,c)$ such that
    the points $p,f(x_1),f(x_2)$ are noncollinear.
    Then there exists $x_1'\in(a,b)$ and $x_2'\in(b,c)$ such that
    the points $p,f(x_1'),f(x_2')$ are noncollinear.
\end{lemma}

\begin{proof}
    Suppose that for all $x_1'\in(a,b)$ and $x_2'\in(b,c)$,
    the points $p,f(x_1'),f(x_2')$ are collinear.
    Then we have $x_1,x_2\in A$ where
    $A$ is either $(a,b)$ or $(b,c)$. Let $B$ be the other interval.
    Since $f$ is nonconstant, there exists $x_0\in B$
    such that $f(x_0)\ne p$. But $f(x_0)$ cannot be collinear
    with $p,f(x_1)$ and with $p,f(x_2)$ at the same time.
\end{proof}

\begin{theorem}
    \label{thm:main}
    A convex closed curve is simple iff it does not lie on a line.
\end{theorem}

\begin{proof}
    The image of a simple closed curve is homeomorphic to
    $\mathbb{S}^1$ and thus cannot be one-dimensional.
    Let $\gamma$ be a convex closed curve in $\mathbb{E}^2$
    which is not simple and does not lie on a line.
    Let $X:=[x_1,x_1+p)$ be a period of $\gamma$ such that
    $\gamma(x_1)=\gamma(x_1')$ for some $x_1'\in(x_1,x_1+p)$.
    Then there exists $x_2,x_3\in(x_1,x_1')\cup(x_1',x_1+p)$
    such that the points $\gamma(x_1),\gamma(x_2),\gamma(x_3)$ are
    noncollinear. By Lemma \ref{lem} we may assume that
    $x_2\in(x_1,x_1')$ and $x_3\in(x_1',x_1+p)$.
    Now let $P$ be any period of $\gamma$. Then there exists
    $c_1,c_2,c_1',c_3\in P$ such that $\gamma(c_1)=\gamma(c_1')$,
    that $c_1<c_2<c_1'$, and that the points
    $p_1:=\gamma(c_1),p_2:=\gamma(c_2),p_3:=\gamma(c_3)$ are noncollinear.
    Let $u\in\mathbb{S}^1$ be a vector perpendicular to
    $\overline{p_1p_3}$. Then we have
    $u\cdot\gamma(c_1)=u\cdot\gamma(c_1')=u\cdot\gamma(c_3)
        \ne u\cdot\gamma(c_2)$, a contradiction to convexity.
\end{proof}

\section{Geometrical Consideration}
\label{sec:geometrical_consideration}

\begin{definition}[Parameterizations]
    Let $\gamma$ be a closed curve in $\mathbb{E}^n$,
    and let $C\subset\mathbb{R}^n$.
    We say that $\gamma$ is a \emph{parameterization}
    of $C$ iff the image of $\gamma$ is $C$.
    Two closed curves are said to be
    \emph{reparameterizations} of each other
    iff their images equal.
\end{definition}

\begin{proposition}
    \label{pro:light_repar}
    Every closed curve has a light reparameterization.
\end{proposition}

\begin{proof}
    The claim follows from \cite[Corollary 13.4]{nadler}
    by viewing maps $f:\mathbb{S}^1\to\mathbb{R}^n$
    as maps $f:[0,1]\to\mathbb{R}^n$ with $f(0)=f(1)$.
\end{proof}

\begin{definition}[Simple sets]
    Let $C\subset\mathbb{R}^n$.
    We say that $C$ is \emph{simple}
    iff $C$ is homeomorphic to
    the unit circle $\mathbb{S}^1$.
\end{definition}

\begin{proposition}
    \label{pro:simple_par}
    A simple subset of $\mathbb{R}^n$ has
    a simple parameterization.
\end{proposition}

\begin{proof}
    Let $C$ be a simple subset of $\mathbb{R}^n$.
    Then there exists a continuous injection
    $f:\mathbb{S}^1\to\mathbb{R}^n$ of image $C$.
    Let $g:\mathbb{R}\to\mathbb{S}^1$ be the function
    $g(t):=(\cos t,\sin t)$. We know that $g$ is continuous
    on $\mathbb{R}$ and periodic with period $2\pi$, and that
    the restriction $g|_{[0,2\pi)}$ is injective.
    Let $\gamma:\mathbb{R}\to\mathbb{R}^n$ be the function
    $f\circ g$. Then $\gamma$ is continuous
    on $\mathbb{R}$ and periodic with period $2\pi$, and the
    restriction $\gamma|_{[0,2\pi)}$ is injective.
    It follows from Proposition \ref{pro:simple_suf_cond}
    that $\gamma$ is a simple closed curve of image $C$.
\end{proof}

\begin{definition}[Weakly convex sets]
    Let $C\subset\mathbb{R}^2$. We say that $C$ is \emph{weakly convex}
    iff for every line $L\subset\mathbb{R}^2$, the set $C\cap L$
    either has cardinality $\le2$ or is a nondegenerate line segment.
\end{definition}

\begin{proposition}
    \label{pro:simple_convex}
    A simple closed curve of weakly convex image is convex.
\end{proposition}

\begin{proof}
    Let $\gamma$ be a simple closed curve of weakly convex image $C$,
    and let $L\subset\mathbb{R}^2$ be any line.
    Since $C$ is weakly convex, the set $C\cap L$
    either has cardinality $\le2$ or is a nondegenerate line segment.
    Since $\lring{\gamma}$ is a homeomorphism by Proposition
    \ref{pro:simple_equiv}, the inverse image $\lring{\gamma}^{-1}(L)$
    either has cardinality $\le2$ or is infinite and connected.
    Thus $\gamma$ is convex by definition.
\end{proof}

\begin{definition}[Irreducibility]
    Let $\gamma$ be a closed curve of image $C$.
    We say that $\gamma$ is \emph{irreducible} iff for every period
    $P$ of $\gamma$ and every closed interval $[a,b]\subset P$
    with $\gamma(a)=\gamma(b)$, we have
    $\gamma([a,b])\ne C$.
\end{definition}

Being irreducible means that the curve does not contain
``redundant loops'' which do not contribute to its image
and can thus be removed. We now proceed to establish
that every closed curve may be reparameterized to be
irreducible, laying the groundwork for our main conjecture.

\begin{lemma}
    \label{lem:irr_exists}
    Every closed curve has an irreducible reparameterization.
\end{lemma}

\begin{proof}
    To be written.
\end{proof}

\begin{conjecture}
    \label{con:irr_linear_convex}
    An irreducible closed curve that lies on a line is convex.
\end{conjecture}

\begin{proof}[Sketch of proof]
    Let $\gamma$ be a closed curve in $\mathbb{E}^1$ which is
    not convex. By Proposition \ref{pro:convex_preserved},
    it suffices to show that $\gamma$ is not irreducible.
\end{proof}

\begin{conjecture}
    \label{con:irr_simple}
    An irreducible closed curve of simple image is simple.
\end{conjecture}

We then present three correlated conjectures, the last one
being our main conjecture, the geometrical analogue to
our main theorem.

\begin{conjecture}
    \label{con:irr_convex}
    An irreducible closed curve of weakly convex image is convex.
\end{conjecture}

\begin{proof}[Proof that
        $\ref{con:irr_linear_convex}
            \land\ref{con:irr_simple}
            \land\ref{con:main}
            \implies\ref{con:irr_convex}$]
    \sloppy
    Let $\gamma$ be an irreducible closed curve of weakly convex
    image $C$. If $C$ is a subset of a line, then $\gamma$
    is convex by Conjecture \ref{con:irr_linear_convex}.
    If $C$ is not a subset of a line,
    then we have $C$ simple by Conjecture \ref{con:main},
    $\gamma$ simple by Conjecture \ref{con:irr_simple},
    and thus $\gamma$ convex by Proposition \ref{pro:simple_convex}.
\end{proof}

\begin{conjecture}
    \label{con:convex}
    Let $C$ be the image of a closed curve. If $C$ is weakly convex,
    then $C$ has a convex parameterization.
\end{conjecture}

\begin{proof}[Proof that $\ref{con:irr_convex}
            \implies\ref{con:convex}$]
    By Lemma \ref{lem:irr_exists} there exists an irreducible
    parameterization of $C$,
    which is convex by Conjecture \ref{con:irr_convex}.
\end{proof}

\begin{proof}[Proof that $\ref{con:main}\implies\ref{con:convex}$]
    If $C$ is not simple, then by Conjecture
    \ref{con:main} we know that $C$ is a subset of a line,
    which certainly is a line segment and has a convex parameterization.
    If $C$ is simple, then by Proposition \ref{pro:simple_par}
    there exists a simple parameterization of $C$,
    which is convex by Proposition \ref{pro:simple_convex}.
\end{proof}

\begin{conjecture}
    \label{con:main}
    Let $C$ be the image of a closed curve.
    Suppose that $C$ is weakly convex.
    Then $C$ is simple iff $C$ is not a subset of a line.
\end{conjecture}

\begin{proof}[Proof that $\ref{con:convex}\implies\ref{con:main}$]
    Clearly, a subset of a line cannot be simple.
    Suppose that $C$ is not a subset of a line. By Conjecture
    \ref{con:convex} there exists a convex parameterization
    $\gamma$ of $C$. Then we have $\gamma$ simple by
    Theorem \ref{thm:main}, and thus $C$ simple by
    Proposition \ref{pro:simple_equiv}.
\end{proof}

\begin{thebibliography}{9}

    \bibitem{milnor}
    J. W. Milnor,
    \emph{On the total curvature of knots},
    Ann. of Math.
    \textbf{52} (1950), no. 2, 248--257.

    \bibitem{nadler}
    S. B. Nadler, Jr.,
    \emph{Continuum Theory: An Introduction},
    CRC Press, Boca Raton, 1992.

\end{thebibliography}

\end{document}